---
title       : MyCalculator
subtitle    : R Shiny Application 
author      : Naveen Silvester
job         : Data Scientist
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Slide 2: Introduction to My Calculator
<a href="https://naveensilvester.shinyapps.io/MyCalculator/">MyCalculator</a> is an application developed in R shiny. This application enables user to enter two numbers and apply mathematical operations on it. Three mathematical
operations are provided as choice. The default is Addition. The results from the mathematical operations is printed on to the main panel. The main panel also provides the option to see
the Documentation/User Guide on checking the checkbox provided in the left side panel.
Click here to experience <a href="https://naveensilvester.shinyapps.io/MyCalculator/">MyCalculator.</a><br>
Here are the list of input variables
 1.  First Number
 2.  Second Number
 3.  Mathematical Operator (Default Addition)
 4.  Citation (Default is Yes)
 5.  Documentation/UserGuid (Default is No)

---
## Slide 3: Mathematical Method - Addition
```{r}
    First_number <- 10
    Second_number <- 20
    sum(First_number + Second_number)
```

---
## Slide 4: Mathematical Method - Subtraction
```{r}
    First_number <- 100
    Second_number <- 20
    subtraction <- (First_number - Second_number)
    subtraction
```

---
## Slide 5: Mathematical Method - Multiplicatoin
```{r}
    First_number <- 10
    Second_number <- 25
    product <- (First_number * Second_number)
    product
```
